%-------------------------
% Resume in Latex
% Author : BISWASH KAPHLE
%------------------------

\input{glyphtounicode}
\pdfgentounicode=1

\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage{tabularx}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Biswash Kaphle}}
 \end{center}
 \\ 
 \vspace*{-10pt}
         bishwas920@gmail.com    
    \hspace{61}
         $\https www.linkedin.com/in/biswashk920/            
    \hspace{70} 
        $\ +977 9846914106\\
\vspace*{5pt}

%==== Experience ====%
\header{Education}
\vspace{1mm}

\textbf{Paschimanchal Campus, IOE, Tribhuwan University} \hfill Pokhara, Nepal\\
\textit{Bachelor of Civil Engineering} \hfill May,2021-Present\\
\vspace{-1mm}\newline.

\end{itemize}
\textbf{Shree Amarsingh Secondary School} \hfill Pokhara,Nepal\\
\textit{Grade 11,12; GPA-3.69/4(9.23/10)} \hfill June,2018 - June,2020\\
\vspace{-1mm}\newline.

\end{itemize}
\textbf{Pioneers' English Boarding School} \hfill Syangja,Nepal\\
\textit{Secondary Education Examination(SEE); GPA-3.85/4(9.63/10) } \hfill -April,2018\\
\vspace{-1mm}\newline.

\end{itemize}


%==== Skills ====%
\header{Experience}
\textbf{Tutor} \hfill Pokhara,Nepal\\
\textit{Maths,Physics(8-12,Part Time)} \hfill 2018 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Dedicated and results-oriented tutor with a proven track record of success in guiding students to achieve academic excellence in mathematics and physics up to grade 12. 
	\item Skilled in tailoring lessons to individual learning styles, I am committed to helping students build strong foundational knowledge, critical thinking skills, and confidence in their abilities. 
\end{itemize}
\textbf{Engineering Drawing} \hfill Remote\\
\textit{Municipal Drawings} \hfill 2022 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Experienced in crafting precise municipal drawings using AutoCAD, adept at translating architectural plans into detailed and accurate digital representations. Proficient in leveraging AutoCAD's tools to ensure compliance with municipal regulations, delivering clear and comprehensive drawings for different agencies.
\end{itemize}

\textbf{Engineering Survey} \hfill Part time\\
\textit{Road and Bridge Survey} \hfill 2023 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Conducting precise engineering surveys, I skillfully employ various instruments and technique to map and analyze terrain, ensuring accurate data for construction projects. Collaborating with multidisciplinary teams, I translated survey findings into comprehensive reports, contributing to the seamless execution of engineering endeavors.
\vspace{2mm}

%==== Projects ====%
\header{Skills} 
\vspace*{-5mm}
\textbf{ \item AutoCAD} \hfill 
\vspace*{-1mm}
\textbf{\item M.S.Excel}
\vspace*{-1mm}
\textbf{\item M.S.Word}
\vspace*{-1mm}
\textbf{\item C Programming}
\vspace*{-1mm}
\textbf{\item Hec-RAS}
\vspace*{-1mm}
\textbf{\item Revit}
\vspace*{2mm}\newline.
%==== Awards ====%
\header{Participation and Awards}
\textbf{Mixed Design Competition} \hfill \\
Secured 1st Position in Mixed Design Competition while in third Year organized by Civil Engineering Student Society;Pashchimanchal Campus  \hfill 2023\\
\vspace*{2mm}
\textbf{Paper Bridge Competition} \hfill \\
Won Paper Bridge Competition while in Second Year organized by Civil Engineering Student Society;Pashchimanchal Campus \hfill 2022\\
\vspace*{2mm}

\textbf{National Maths Olympiad} \hfill \\
Participant(Top 25) \hfill 2019\\
\vspace*{2mm}

%==== Ongoing Projects ====%
\header{Ongoing Works}
\textbf{Research Paper} \hfill \\
Title:"Assesment of the capacity of roadside drainage on Lamachour road. " as principle researcher.\hfill 2023\\
\vspace*{2mm}
\textbf{Research Paper} \hfill \\
Title:"Evaluation of Effectiveness LID for Roadside Flood Mitigation in a Monsoon-Dominant Mountain Valley in the Mid-Himalayan Region of Nepal." as Intern. \hfill 2023\\
\vspace*{2mm}

\ 
\end{document}


